### 2017-12-01 manuscript.rmd
fixed species names in manuscript code calls

```{r char_evo_setup, include=F, echo=F}
#Load data
read.csv('character_coding/main_characters.csv', header = T, sep = ',') -> cdata
cdata$Species = str_replace_all(cdata$Species, "sp ", "sp")
rownames(cdata) = cdata$Species

@@

#Clean Raw Data
names(raw_data)[1] = "Species"
raw_data$Species = as.character(raw_data$Species)
raw_data$Species[which(raw_data$Species == "Kephyes")] = "Kephyes ovata"
raw_data$Species[which(raw_data$Species == "Lilyopsis")] = "Lilyopsis fluoracantha"
raw_data$Species[which(raw_data$Species == "Agalma")] = "Agalma elegans"
raw_data$Species[which(raw_data$Species == "Frillagalma")] = "Frillagalma vityazi"
raw_data$Species[which(raw_data$Species == "Stephalia")] = "Stephalia dilata"
raw_data$Species[which(raw_data$Species == "Lychnagalma")] = "Lychnagalma utricularia"
raw_data$Species[which(raw_data$Species == "Craseoa")] = "Craseoa lathetica"
raw_data$Species[which(raw_data$Species == "Cordagalma")] = "Cordagalma sp"
raw_data$Species[which(raw_data$Species == "Desmophyes haematogaster")] = "Prayidae D27SS7"
raw_data$Species[which(raw_data$Species == "Craseoa lathetica")] = "Prayidae D27D2"
raw_data$Species[which(raw_data$Species == "Rudjakovia")] = "Rudjakovia sp"
raw_data$Species[which(raw_data$Species == "Thermopalia")] = "Thermopalia sp"
raw_data$Species[which(raw_data$Species == "Physonectae sp. 1")] = "Physonect sp"

@@

sp_order = c("Agalma elegans", "Athorybia rosacea", "Halistemma rubrum", "Nanomia bijuga", "Lychnagalma utricularia", "Physophora gilmeri", "Forskalia asymmetrica", "Cordagalma sp", "Resomia ornicephala", "Frillagalma vityazi", "Physonect sp", "Marrus claudanielis", "Stephalia dilata", "Thermopalia sp", "Erenna richardi", "Abylopsis tetragona", "Diphyes dispar", "Chelophyes appendiculata", "Kephyes ovata", "Chuniphyes multidentata", "Lilyopsis fluoracantha", "Prayidae D27D2", "Prayidae D27SS7", "Hippopodius hippopus", "Bargmannia amoena", "Bargmannia elongata", "Bargmannia lata", "Rudjakovia sp", "Apolemia rubriversa", "Apolemia lanosa", "Apolemia sp", "Rhizophysa filiformis", "Physalia physalis")

>>>>

```{r char_evo_setup, include=F, echo=F}
#Load data
read.csv('character_coding/main_characters.csv', header = T, sep = ',') -> cdata
rownames(cdata) = cdata$Species

@@

#Clean Raw Data
names(raw_data)[1] = "Species"
raw_data$Species = as.character(raw_data$Species)
raw_data$Species[which(raw_data$Species == "Kephyes")] = "Kephyes ovata"
raw_data$Species[which(raw_data$Species == "Lilyopsis")] = "Lilyopsis fluoracantha"
raw_data$Species[which(raw_data$Species == "Agalma")] = "Agalma elegans"
raw_data$Species[which(raw_data$Species == "Frillagalma")] = "Frillagalma vityazi"
raw_data$Species[which(raw_data$Species == "Stephalia")] = "Stephalia dilata"
raw_data$Species[which(raw_data$Species == "Lychnagalma")] = "Lychnagalma utricularia"
raw_data$Species[which(raw_data$Species == "Craseoa")] = "Craseoa lathetica"
raw_data$Species[which(raw_data$Species == "Cordagalma")] = "Cordagalma sp."
raw_data$Species[which(raw_data$Species == "Desmophyes haematogaster")] = "Desmophyes sp."
raw_data$Species[which(raw_data$Species == "Rudjakovia")] = "Rudjakovia sp."
raw_data$Species[which(raw_data$Species == "Thermopalia")] = "Stephalia sp." ##We should do something about this not corresponding...
raw_data$Species[which(raw_data$Species == "Physonectae sp. 1")] = "Undescribed Sp. L" #Is this correct?

@@

sp_order = c("Agalma elegans", "Athorybia rosacea", "Halistemma rubrum", "Nanomia bijuga", "Lychnagalma utricularia", "Physophora gilmeri", "Forskalia asymmetrica", "Cordagalma sp.", "Resomia ornicephala", "Frillagalma vityazi", "Undescribed Sp. L", "Marrus claudanielis", "Stephalia dilata", "Stephalia sp.", "Erenna richardi", "Abylopsis tetragona", "Diphyes dispar", "Chelophyes appendiculata", "Kephyes ovata", "Chuniphyes multidentata", "Lilyopsis fluoracantha", "Craseoa lathetica", "Desmophyes sp.", "Hippopodius hippopus", "Bargmannia amoena", "Bargmannia elongata", "Bargmannia lata", "Rudjakovia sp", "Apolemia rubriversa", "Apolemia lanosa", "Apolemia sp.", "Rhizophysa filiformis", "Physalia physalis")
